---
title: "Les pingouins ont-ils froid ?"
subtitle: "Un exemple de document Quarto"
author: "Diane & Teo"
date: today
toc: true
code-annotations: hover
---

# Quarto

  links:
    - icon: github
      text: Github Teo
      href: https://github.com/teodoromouniertebas
    - icon: linkedin
      text: Linkedin Teo
      href: https://www.linkedin.com/in/teodoro-mounier-tebas-a423341a3/
    - icon: github
      text: Github Diane
      href: https://github.com/dianethy
    - icon: linkedin
      text: Linkedin Diane
      href: https://www.linkedin.com/in/diane-thierry-b22099193/



## Running Code

{{< lipsum 1 >}}

### mon titre 3

{{< lipsum 1 >}}

#### header 4

{{< lipsum 1 >}}



> When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this. When you click the **Render** button a document will be generated that includes both content and the output of embedded code. 

{{< lipsum 1 >}}

```{r}
radius <- 5
#ceci est un commentaire
```

#### bblabla 
When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:


### Running Code bis
When you click the **Render** button a document will be generated that `{r} radius` includes both content and the output of embedded code. You can embed code like this:



## Running Code

### blblbk

::: {.callout-note}
Note that there are five types of callouts, including:
`note`, `warning`, `important`, `tip`, and `caution`.
:::

::: {.callout-tip}
## conseil

This is an example of a callout with a title.
:::

::: {.callout-caution}
## prudence

This is an example of a callout with a title.
:::


::: {.callout-warning}
## avertissement

This is an example of a callout with a title.
:::

::: {.callout-important}
## important

This is an example of a callout with a title.
:::




```{r}
radius <- 5
```

### blblbk
When you click the **Render** button a document will be generated that `{r} radius` includes both content and the output of embedded code. You can embed code like this:


# Rstudio

```{r}
#| message: false
#| warning: false
#| eval: false
library(tidyverse)
library(palmerpenguins)
penguins |>                                      # <1>
  mutate(                                        # <2>
    bill_ratio = bill_depth_mm / bill_length_mm, # <2>
    bill_area  = bill_depth_mm * bill_length_mm  # <2>
  )                                              # <2>
```
1. Take `penguins`, and then,
2. add new columns for the bill ratio and bill area.


## Running Code
### Running Code
When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

### Running Code bis
When you click the **Render** button a document will be generated that `{r} radius` includes both content and the output of embedded code. You can embed code like this: